---
title: "<center> Response to a gradient of environmental cues in mesotaenium endlicherianum<center>"
author: "<center> Armin Dadras <center><br>"
date: "<center> _`r Sys.Date()`_ <center>"
output:
  html_document:
    code_folding: hide
    df_print: paged
    theme: yeti
    highlight: tango
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
  pdf_document:
    fig_caption: yes
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(rmarkdown)
library(tinytex)
library(knitr)
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

------------------------------------------------------------------------

# Importing data into R

After read mapping with HISAT2, [TxImport](https://bioconductor.org/packages/release/bioc/html/tximport.html) was used to read Stringtie outputs into the R environment. Annotation data was used to summarize data from transcript-level to gene-level.

```{r Step 1: Importing count data into R}
library(tidyverse) # provides access to Hadley Wickham's collection of R packages for data science
library(tximport)
library(edgeR)
library(matrixStats)
library(cowplot)
library(rhdf5)

targets <- read.csv("study_design.csv", header = T)

## Determine samples I am interested in
#targets <- targets %>%
#    filter(targets$condition_not_to_use %in% (c("standard_growth", "heat")))

sampleLabels <- targets$sample_name
path <- file.path("kallisto",paste0(targets$sample_id), "abundance.h5") 
#check if files exist for all samples in study design file
Tx <- read_tsv("tx2gene.tsv")

Txi_gene <- tximport(path,
         type = "kallisto",
         countsFromAbundance = "lengthScaledTPM",
         tx2gene = Tx,
         txOut = F,
         ignoreTxVersion = F)
```

------------------------------------------------------------------------

# Preprocessing

## Impact of filtering and normalization

The abundance data are TPM, while the counts are read counts mapping to each gene or transcript.

```{r Step 2: Impact of filtering and normalization}
myDGEList <- DGEList(Txi_gene$counts) # Make a DGElist from the counts
log2.cpm <- cpm(myDGEList, log=TRUE) # use the 'cpm' function from EdgeR to get counts per million
log2.cpm.df <- as_tibble(log2.cpm, rownames = "geneID")
colnames(log2.cpm.df) <- c("geneID", sampleLabels)
log2.cpm.df.pivot <- pivot_longer(log2.cpm.df, # dataframe to be pivoted
                                  cols = 2:(length(sampleLabels)+1), # column names to be stored as a SINGLE variable
                                  names_to = "samples", # name of that new variable (column)
                                  values_to = "expression") # name of new variable (column) storing all the values (data)

p1 <- ggplot(log2.cpm.df.pivot) +
  aes(x=samples, y=expression, fill=samples) +
  geom_violin(trim = FALSE, show.legend = FALSE) +
  stat_summary(fun = "median",
               geom = "point",
               shape = 95,
               size = 10,
               color = "black",
               show.legend = FALSE) +
  labs(y="log2 expression", x = "sample",
       title="Log2 Counts per Million (CPM)",
       subtitle="unfiltered, non-normalized",
       caption=paste0("produced on ", Sys.time())) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 8),
        plot.subtitle = element_text(size = 6))

# Filter myDGEList
cpm <- cpm(myDGEList)
# The line below is important! This is where the filtering starts
keepers <- rowSums(cpm>1)>=3 #user defined
myDGEList.filtered <- myDGEList[keepers,]

log2.cpm.filtered <- cpm(myDGEList.filtered, log=TRUE)
log2.cpm.filtered.df <- as_tibble(log2.cpm.filtered, rownames = "geneID")
colnames(log2.cpm.filtered.df) <- c("geneID", sampleLabels)
log2.cpm.filtered.df.pivot <- pivot_longer(log2.cpm.filtered.df, # dataframe to be pivoted
                                           cols = 2:(length(sampleLabels)+1), # column names to be stored as a SINGLE variable
                                           names_to = "samples", # name of that new variable (column)
                                           values_to = "expression") # name of new variable (column) storing all the values (data)

p2 <- ggplot(log2.cpm.filtered.df.pivot) +
  aes(x=samples, y=expression, fill=samples) +
  geom_violin(trim = FALSE, show.legend = FALSE) +
  stat_summary(fun = "median",
               geom = "point",
               shape = 95,
               size = 10,
               color = "black",
               show.legend = FALSE) +
  labs(y="log2 expression", x = "sample",
       title="Log2 Counts per Million (CPM)",
       subtitle="filtered, non-normalized",
       caption=paste0("produced on ", Sys.time())) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 8),
        plot.subtitle = element_text(size = 6))

# Normalize the data
myDGEList.filtered.norm <- calcNormFactors(myDGEList.filtered, method = "TMM")
log2.cpm.filtered.norm <- cpm(myDGEList.filtered.norm, log=TRUE)
log2.cpm.filtered.norm.df <- as_tibble(log2.cpm.filtered.norm, rownames = "geneID")
colnames(log2.cpm.filtered.norm.df) <- c("geneID", sampleLabels)
log2.cpm.filtered.norm.df.pivot <- pivot_longer(log2.cpm.filtered.norm.df, # dataframe to be pivoted
                                                cols = 2:(length(sampleLabels)+1), # column names to be stored as a SINGLE variable
                                                names_to = "samples", # name of that new variable (column)
                                                values_to = "expression") # name of new variable (column) storing all the values (data)

p3 <- ggplot(log2.cpm.filtered.norm.df.pivot) +
  aes(x=samples, y=expression, fill=samples) +
  geom_violin(trim = FALSE, show.legend = FALSE) +
  stat_summary(fun = "median",
               geom = "point",
               shape = 95,
               size = 10,
               color = "black",
               show.legend = FALSE) +
  labs(y="log2 expression", x = "sample",
       title="Log2 Counts per Million (CPM)",
       subtitle="filtered, TMM normalized",
       caption=paste0("produced on ", Sys.time())) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 8),
        plot.subtitle = element_text(size = 6))

ggsave(filename = "plots/impact_of_filtering_and_normalization.pdf", plot_grid(p1, p2, p3, labels = c('A', 'B', 'C'), label_size = 12, ncol = 3, align = "hv"), width = 20, height = 20)
plot_grid(p1, p2, p3, labels = c('A', 'B', 'C'), label_size = 12, ncol = 3, align = "hv")

```

------------------------------------------------------------------------

Filtering was carried out to remove lowly expressed genes. Genes with less than 1 count per million (CPM) in at least 3 or more samples filtered out. This reduced the number of genes from `r nrow(myDGEList)` to `r nrow(myDGEList.filtered.norm)`.

------------------------------------------------------------------------

## Table of filtered and normalized data

The table that includes expression data for `r nrow(myDGEList.filtered.norm)` genes are saved in`tables/heat/filtered_and_TMM_normalized_counts.tsv`.

------------------------------------------------------------------------

```{r Step 3: Table of filtered and normalized data}
mydata.df <- log2.cpm.filtered.norm.df %>%
  mutate_if(is.numeric, round, 2)

write_tsv(mydata.df, "tables/filtered_and_TMM_normalized_counts.tsv")
```

------------------------------------------------------------------------

# Model the mean-variance relationship

```{r Step 5.1: Model the mean-variance relationship}
library(limma)
library(gt)
library(DT)
library(plotly)

group <- targets$FvFM_1
group <- factor(group)
group <- relevel(group, ref = "Control")

design <- model.matrix(~0 + group)
colnames(design) <- c(levels(group))
colnames(myDGEList.filtered.norm) <- sampleLabels

# Use VOOM function from Limma package to model the mean-variance relationship
v.DEGList.filtered.norm <- voom(myDGEList.filtered.norm, design,
                                plot = TRUE)
v.DEGList.filtered.norm_E.df <- as_tibble(v.DEGList.filtered.norm$E,
                                          rownames = "geneID")

corfit <- duplicateCorrelation(v.DEGList.filtered.norm, ndups = 1, block = targets$biolrep)


fit <- lmFit(v.DEGList.filtered.norm, design, block = targets$biolrep, cor = corfit$consensus)


contrast.matrix <- makeContrasts(TvsC = Treatment-Control,
                                 levels=design)

fits <- contrasts.fit(fit, contrast.matrix)
ebFit <- eBayes(fits)

myTopHits <- topTable(ebFit, adjust ="BH", coef=1, number=40000, sort.by="logFC")
myTopHits.df <- myTopHits %>%
  as_tibble(rownames = "geneID")


results <- decideTests(ebFit, method="global", adjust.method="BH", p.value=0.01, lfc=1)
colnames(v.DEGList.filtered.norm$E) <- sampleLabels

diffGenes <- v.DEGList.filtered.norm$E[results[,1] !=0, ]


diffGenes.df <- as_tibble(diffGenes, rownames = "geneID")

write_tsv(diffGenes.df, "tables/expression_of_DEGs_FvFm.tsv")


library(tidyverse)
library(gplots)
library(RColorBrewer)
library(pheatmap)
myheatcolors <- rev(brewer.pal(name="RdBu", n=11))

# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

pheatmap(as.matrix(diffGenes.df[,-1]),
        na.rm = F,
        na_col = "black",
        cluster_cols = T, cluster_rows = T,
        color=myheatcolors, scale='row', labRow=NA,
        cexRow=1, cexCol=1, margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()
```

```{r volcano plot}
# Volcano Plots ----
# in topTable function above, set 'number=40000' to capture all genes

# now plot
p1 <- ggplot(myTopHits.df) +
  aes(y=-log10(adj.P.Val), x=logFC, text = paste("Symbol:", geneID)) +
  geom_point(size=2) +
  geom_hline(yintercept = -log10(0.01), linetype="longdash", colour="grey", size=1) +
  geom_vline(xintercept = 1, linetype="longdash", colour="#BE684D", size=1) +
  geom_vline(xintercept = -1, linetype="longdash", colour="#2C467A", size=1) +
  annotate("rect", xmin = 1, xmax = 15, ymin = -log10(0.01), ymax = 35, alpha=.2, fill="#7bdff2") +
  annotate("rect", xmin = -1, xmax = -15, ymin = -log10(0.01), ymax = 35, alpha=.2, fill="#f2b5d4") +
  labs(title="Volcano plot",
       subtitle = "FvFm treatment vs. FvFm control",
       caption=paste0("produced on ", Sys.time())) +
  theme_bw()


ggsave(filename = "plots/volcano_plots_FvFM.pdf", plot_grid(p1), width = 20, height = 20)
plot_grid(p1)
```


```{r DEGs FvFm}
myheatcolors <- rev(brewer.pal(name="RdBu", n=10))
clustRows <- hclust(as.dist(1-cor(t(diffGenes), method="pearson")), method="complete") #cluster rows by pearson correlation
clustColumns <- hclust(as.dist(1-cor(diffGenes, method="spearman")), method="complete")
module.assign <- cutree(clustRows, k=2)
module.color <- rainbow(length(unique(module.assign)), start=0.1, end=0.9) 
module.color <- module.color[as.vector(module.assign)]

# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

# Step 2: Create the plot with R code
heatmap.2(diffGenes, 
          Rowv=as.dendrogram(clustRows), 
          Colv=as.dendrogram(clustColumns),
          RowSideColors=module.color,
          col=myheatcolors, scale='row', labRow=NA,
          density.info="none", trace="none",  
          cexRow=1, cexCol=1, margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()



modulePick <- 2 
myModule_2 <- diffGenes[names(module.assign[module.assign %in% modulePick]),] 
hrsub_2 <- hclust(as.dist(1-cor(t(myModule_2), method="pearson")), method="complete")
clustColumns <- hclust(as.dist(1-cor(myModule_2, method="spearman")), method="complete")
myModule_2.df <- as_tibble(myModule_2, rownames = "geneID")
write_tsv(myModule_2.df, "tables/FvFm/module_2_genes.tsv")

# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm/module_2.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

# Step 2: Create the plot with R code
heatmap.2(myModule_2, 
          Rowv=as.dendrogram(hrsub_2), 
          Colv=clustColumns, 
          labRow = NA,
          col=myheatcolors, scale="row", 
          density.info="none", trace="none", 
          RowSideColors=module.color[module.assign%in%modulePick], margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()



modulePick <- 1 
myModule_1 <- diffGenes[names(module.assign[module.assign %in% modulePick]),] 
hrsub_1 <- hclust(as.dist(1-cor(t(myModule_1), method="pearson")), method="complete")
clustColumns <- hclust(as.dist(1-cor(myModule_1, method="spearman")), method="complete")
myModule_1.df <- as_tibble(myModule_1, rownames = "geneID")
write_tsv(myModule_1.df, "tables/FvFm/module_1_genes.tsv")


# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm/module1.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

# Step 2: Create the plot with R code

heatmap.2(myModule_1, 
          Rowv=as.dendrogram(hrsub_1), 
          Colv=clustColumns, 
          labRow = NA,
          col=myheatcolors, scale="row", 
          density.info="none", trace="none", 
          RowSideColors=module.color[module.assign%in%modulePick], margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()
```

```{r Step 6: Enrichment FvFm}
library(clusterProfiler)
library(enrichplot)
library(tidyverse)

term2gene <- read.csv2("term2gene_GO.csv")
term2gene <- term2gene[,-1] # remove the first index row
term2name <- read.csv2("term2name_GO.csv")
term2name <- term2name[,-1] # remove the first index row

my_universe <- term2gene[term2gene$gene %in% v.DEGList.filtered.norm_E.df$geneID,]

## Up regulated
enrichment <- enricher(rownames(myModule_2),
                       TERM2GENE = term2gene,
                       TERM2NAME = term2name,
                       pvalueCutoff = 0.01,
                       universe = my_universe$gene,
                       qvalueCutoff = 0.01)
#save the enrichment result
write.csv(file = paste0("plots/heatmaps/FvFm/module2_enrichment.csv"), x = enrichment@result)
    
if (any(enrichment@result$p.adjust <= 0.01)){
    p <- dotplot(enrichment,
                 x= "geneRatio", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 color="p.adjust",
                 orderBy = "x", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 showCategory=50,
                 font.size=8) +
        ggtitle("dotplot for ORA")
    
    ggsave(filename = paste0("plots/heatmaps/FvFm/module2_dotplot.pdf"),
           plot =  p,  dpi = 600, width = 40, height = 40, units = "cm")
    
    p <- cnetplot(enrichment,
                  node_label="all",
                  showCategory = 30,
                  colorEdge = TRUE,
                  cex_label_gene = 0.5,
                  cex_label_category=0.5,
                  layout = "kk")
    ggsave(filename = paste0("plots/heatmaps/FvFm/module2_cnetplot.pdf"),plot =  p,  dpi = 600,
               width =  60, height = 40, units = "cm")
}

## Down regulated
enrichment <- enricher(rownames(myModule_1),
                       TERM2GENE = term2gene,
                       TERM2NAME = term2name,
                       pvalueCutoff = 0.01,
                       universe = my_universe$gene,
                       qvalueCutoff = 0.01)
#save the enrichment result
write.csv(file = paste0("plots/heatmaps/FvFm/module1_enrichment.csv"), x = enrichment@result)
    
if (any(enrichment@result$p.adjust <= 0.01)){
    p <- dotplot(enrichment,
                 x= "geneRatio", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 color="p.adjust",
                 orderBy = "x", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 showCategory=50,
                 font.size=8) +
        ggtitle("dotplot for ORA")
    
    ggsave(filename = paste0("plots/heatmaps/FvFm/module1_dotplot.pdf"),
           plot =  p,  dpi = 600, width = 40, height = 40, units = "cm")
    
    p <- cnetplot(enrichment,
                  node_label="all",
                  showCategory = 30,
                  colorEdge = TRUE,
                  cex_label_gene = 0.5,
                  cex_label_category=0.5,
                  layout = "kk")
    ggsave(filename = paste0("plots/heatmaps/FvFm/module1_cnetplot.pdf"),plot =  p,  dpi = 600,
               width =  60, height = 40, units = "cm")
}
```

# Model the mean-variance relationship

```{r Step 5.1: Model the mean-variance relationship 2}
library(limma)
library(gt)
library(DT)
library(plotly)

targets <- targets %>%
    mutate(FvFm_2 = ifelse(FvFm_measure >= 0.5, "Control", "Treatment"))

group <- targets$FvFm_2
group <- factor(group)
group <- relevel(group, ref = "Control")

design <- model.matrix(~0 + group)
colnames(design) <- c(levels(group))
colnames(myDGEList.filtered.norm) <- sampleLabels

# Use VOOM function from Limma package to model the mean-variance relationship
v.DEGList.filtered.norm <- voom(myDGEList.filtered.norm, design,
                                plot = TRUE)
v.DEGList.filtered.norm_E.df <- as_tibble(v.DEGList.filtered.norm$E,
                                          rownames = "geneID")

corfit <- duplicateCorrelation(v.DEGList.filtered.norm, ndups = 1, block = targets$biolrep)


fit <- lmFit(v.DEGList.filtered.norm, design, block = targets$biolrep, cor = corfit$consensus)


contrast.matrix <- makeContrasts(TvsC = Treatment-Control,
                                 levels=design)

fits <- contrasts.fit(fit, contrast.matrix)
ebFit <- eBayes(fits)

myTopHits <- topTable(ebFit, adjust ="BH", coef=1, number=40000, sort.by="logFC")
myTopHits.df <- myTopHits %>%
  as_tibble(rownames = "geneID")


results <- decideTests(ebFit, method="global", adjust.method="BH", p.value=0.01, lfc=1)
colnames(v.DEGList.filtered.norm$E) <- sampleLabels

diffGenes <- v.DEGList.filtered.norm$E[results[,1] !=0, ]


diffGenes.df <- as_tibble(diffGenes, rownames = "geneID")

write_tsv(diffGenes.df, "tables/expression_of_DEGs_FvFm_2.tsv")


library(tidyverse)
library(gplots)
library(RColorBrewer)
library(pheatmap)
myheatcolors <- rev(brewer.pal(name="RdBu", n=11))

# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm_2.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

pheatmap(as.matrix(diffGenes.df[,-1]),
        na.rm = F,
        na_col = "black",
        cluster_cols = T, cluster_rows = T,
        color=myheatcolors, scale='row', labRow=NA,
        cexRow=1, cexCol=1, margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()
```

```{r volcano plot}
# Volcano Plots ----
# in topTable function above, set 'number=40000' to capture all genes

# now plot
p1 <- ggplot(myTopHits.df) +
  aes(y=-log10(adj.P.Val), x=logFC, text = paste("Symbol:", geneID)) +
  geom_point(size=2) +
  geom_hline(yintercept = -log10(0.01), linetype="longdash", colour="grey", size=1) +
  geom_vline(xintercept = 1, linetype="longdash", colour="#BE684D", size=1) +
  geom_vline(xintercept = -1, linetype="longdash", colour="#2C467A", size=1) +
  annotate("rect", xmin = 1, xmax = 15, ymin = -log10(0.01), ymax = 35, alpha=.2, fill="#7bdff2") +
  annotate("rect", xmin = -1, xmax = -15, ymin = -log10(0.01), ymax = 35, alpha=.2, fill="#f2b5d4") +
  labs(title="Volcano plot",
       subtitle = "FvFm treatment vs. FvFm control",
       caption=paste0("produced on ", Sys.time())) +
  theme_bw()


ggsave(filename = "plots/volcano_plots_FvFM_2.pdf", plot_grid(p1), width = 20, height = 20)
plot_grid(p1)
```


```{r DEGs FvFm}
myheatcolors <- rev(brewer.pal(name="RdBu", n=10))
clustRows <- hclust(as.dist(1-cor(t(diffGenes), method="pearson")), method="complete") #cluster rows by pearson correlation
clustColumns <- hclust(as.dist(1-cor(diffGenes, method="spearman")), method="complete")
module.assign <- cutree(clustRows, k=2)
module.color <- rainbow(length(unique(module.assign)), start=0.1, end=0.9) 
module.color <- module.color[as.vector(module.assign)]

# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm_2.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

# Step 2: Create the plot with R code
heatmap.2(diffGenes, 
          Rowv=as.dendrogram(clustRows), 
          Colv=as.dendrogram(clustColumns),
          RowSideColors=module.color,
          col=myheatcolors, scale='row', labRow=NA,
          density.info="none", trace="none",  
          cexRow=1, cexCol=1, margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()



modulePick <- 2 
myModule_2 <- diffGenes[names(module.assign[module.assign %in% modulePick]),] 
hrsub_2 <- hclust(as.dist(1-cor(t(myModule_2), method="pearson")), method="complete")
clustColumns <- hclust(as.dist(1-cor(myModule_2, method="spearman")), method="complete")
myModule_2.df <- as_tibble(myModule_2, rownames = "geneID")
write_tsv(myModule_2.df, "tables/FvFm_2/module_2_genes.tsv")

# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm_2/module_2.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

# Step 2: Create the plot with R code
heatmap.2(myModule_2, 
          Rowv=as.dendrogram(hrsub_2), 
          Colv=clustColumns, 
          labRow = NA,
          col=myheatcolors, scale="row", 
          density.info="none", trace="none", 
          RowSideColors=module.color[module.assign%in%modulePick], margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()



modulePick <- 1 
myModule_1 <- diffGenes[names(module.assign[module.assign %in% modulePick]),] 
hrsub_1 <- hclust(as.dist(1-cor(t(myModule_1), method="pearson")), method="complete")
clustColumns <- hclust(as.dist(1-cor(myModule_1, method="spearman")), method="complete")
myModule_1.df <- as_tibble(myModule_1, rownames = "geneID")
write_tsv(myModule_1.df, "tables/FvFm_2/module_1_genes.tsv")


# Step 1: Call the pdf command to start the plot
pdf(file = paste0("plots/heatmaps/FvFm_2/module1.pdf"),   # The directory you want to save the file in
    width = 21, # The width of the plot in inches
    height = 21) # The height of the plot in inches

# Step 2: Create the plot with R code

heatmap.2(myModule_1, 
          Rowv=as.dendrogram(hrsub_1), 
          Colv=clustColumns, 
          labRow = NA,
          col=myheatcolors, scale="row", 
          density.info="none", trace="none", 
          RowSideColors=module.color[module.assign%in%modulePick], margins=c(8,20))

# Step 3: Run dev.off() to create the file!
dev.off()
```

```{r Step 6: Enrichment FvFm}
library(clusterProfiler)
library(enrichplot)
library(tidyverse)

term2gene <- read.csv2("term2gene_GO.csv")
term2gene <- term2gene[,-1] # remove the first index row
term2name <- read.csv2("term2name_GO.csv")
term2name <- term2name[,-1] # remove the first index row

my_universe <- term2gene[term2gene$gene %in% v.DEGList.filtered.norm_E.df$geneID,]

## Up regulated
enrichment <- enricher(rownames(myModule_2),
                       TERM2GENE = term2gene,
                       TERM2NAME = term2name,
                       pvalueCutoff = 0.01,
                       universe = my_universe$gene,
                       qvalueCutoff = 0.01)
#save the enrichment result
write.csv(file = paste0("plots/heatmaps/FvFm_2/module2_enrichment.csv"), x = enrichment@result)
    
if (any(enrichment@result$p.adjust <= 0.01)){
    p <- dotplot(enrichment,
                 x= "geneRatio", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 color="p.adjust",
                 orderBy = "x", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 showCategory=50,
                 font.size=8) +
        ggtitle("dotplot for ORA")
    
    ggsave(filename = paste0("plots/heatmaps/FvFm_2/module2_dotplot.pdf"),
           plot =  p,  dpi = 600, width = 40, height = 40, units = "cm")
    
    p <- cnetplot(enrichment,
                  node_label="all",
                  showCategory = 30,
                  colorEdge = TRUE,
                  cex_label_gene = 0.5,
                  cex_label_category=0.5,
                  layout = "kk")
    ggsave(filename = paste0("plots/heatmaps/FvFm_2/module2_cnetplot.pdf"),plot =  p,  dpi = 600,
               width =  60, height = 40, units = "cm")
}

## Down regulated
enrichment <- enricher(rownames(myModule_1),
                       TERM2GENE = term2gene,
                       TERM2NAME = term2name,
                       pvalueCutoff = 0.01,
                       universe = my_universe$gene,
                       qvalueCutoff = 0.01)
#save the enrichment result
write.csv(file = paste0("plots/heatmaps/FvFm_2/module1_enrichment.csv"), x = enrichment@result)
    
if (any(enrichment@result$p.adjust <= 0.01)){
    p <- dotplot(enrichment,
                 x= "geneRatio", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 color="p.adjust",
                 orderBy = "x", # Options: GeneRatio, BgRatio, pvalue, p.adjust, qvalue
                 showCategory=50,
                 font.size=8) +
        ggtitle("dotplot for ORA")
    
    ggsave(filename = paste0("plots/heatmaps/FvFm_2/module1_dotplot.pdf"),
           plot =  p,  dpi = 600, width = 40, height = 40, units = "cm")
    
    p <- cnetplot(enrichment,
                  node_label="all",
                  showCategory = 30,
                  colorEdge = TRUE,
                  cex_label_gene = 0.5,
                  cex_label_category=0.5,
                  layout = "kk")
    ggsave(filename = paste0("plots/heatmaps/FvFm_2/module1_cnetplot.pdf"),plot =  p,  dpi = 600,
               width =  60, height = 40, units = "cm")
}
```


# Session info

The output from running 'sessionInfo' is shown below and details all packages and version necessary to reproduce the results in this report.

```{r session info}
sessionInfo()
```
